### 2019-11-28 Mathematical Statistics/ms_ch_04.rmd
mathematical statistics, ch4
mathematical statistics, ch4

permutations( v = p, n = 2, r = 2, repeats.allowed = T)

combinations( v = p, n = 3, r = 2, repeats.allowed = T)

@@

p <- c(3, 4, 6, 6)

sample.size <- 2
perm <- permutations( length(p), sample.size, repeats.allowed = T)

d <- data.table( c1 = p[perm[, 1]], c2 = p[perm[, 2]])
d[, m := (c1 + c2) / 2]

@@

@@

@@

What is the probability that the sum is 13 or larger?

>>>>

@@

result = numeric(12)
index <- 1
for(j in 1:length(A))
{
   for(k in 1:length(B))
   {
      result[index] <- A[j] + B[k]
      index <- index + 1
   }
}

sort(result)

@@

Mean of _A_: __`r mean(A)`__. Mean of _B_: __`r mean(B)`__.

Mean of _A + B_: __`r mean(result)`__

@@

mean(A) + mean(B) = mean(A + B).

@@

prob <- sum(result >= 13) / length(result)

What is the probability that the sum is 13 or larger? __`r prob*100`%__

### 4.4

Consider the population {3, 5, 6, 6, 8, 11, 13, 15, 19, 20}.

a.) Compute the mean and standard deviation and create a dot plot of its distribution.

```{r, echo = T, fig.height=3.5, fig.width=8}

p <- c(3, 5, 6, 6, 8, 11, 13, 15, 19, 20)

mu <- mean(p)
sigma <- sd(p)

ggplot(data.table(value = p)) +
   geom_dotplot(aes(value, fill = ..count..), binwidth = 1) +
   labs(title = "Population Dot Plot")

$\mu = `r mu`$, $\sigma = `r sigma`$

b.) Simulate the sampling distribution of $\bar{X}$ by taking random samples of size 4 and plot your results.

```{r, echo = T, fig.height=3.5, fig.width=8}

N <- 10e2
results <- numeric(N)

for( i in 1:N)
{
   index <- sample(length(p), size = 4, replace = F)
   results[i] <- mean( p[index] )
}

ggplot(data.table(value = results)) +
   geom_histogram(aes(value, fill = ..count..), bins = 30) +
   labs(title = "Sample Means")

xbar <- mean(results)
se <- sd(results) / sqrt(N)

Compute the mean and standard error, and compare to the population mean and standard deviation.

mean: `r xbar`, standard error: `r se`

c.) Use the simulation to find $P(\bar{X} < 11)$.

prob <- mean(results < 11)

$P(\bar{X} < 11) = `r prob*100`$%
